\documentclass[10pt]{article}
\usepackage[a4paper,margin=0.78in]{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{url}
\usepackage[numbers,sort&compress]{natbib}

\makeatletter
\IfFileExists{sections/introduction.tex}
  {\newcommand{\srroot}{.}}
  {\IfFileExists{scientific_reports/sections/introduction.tex}
    {\newcommand{\srroot}{scientific_reports}}
    {\newcommand{\srroot}{paper/scientific_reports}}}
\def\input@path{{\srroot/}{\srroot/sections/}{\srroot/tables/}}
\makeatother
\graphicspath{{\srroot/}{\srroot/figures/}}

\title{A reproducible diagnostic benchmark for language-to-target generation in robotic manipulation}
\author{Zhuo Chen\\Correspondence: \href{mailto:zhuoc@chalmers.se}{zhuoc@chalmers.se}}
\date{}

\begin{document}
\maketitle

\begin{abstract}
Language-conditioned manipulation evaluations can obscure failures in converting a query into a 3D target. We present EmbodiedStressBench, a reproducible diagnostic benchmark for the language-to-target stage of robotic manipulation, separating detection-list selection, RGB-D lifting, stressor sensitivity, oracle gaps, and failure labels. In seed-controlled ManiSkill sweeps, target sources showed a threshold-dependent tradeoff: box-center depth was more precise at strict 4--6 cm thresholds, whereas crop-median depth was more robust at the default 8 cm and relaxed 10 cm thresholds. A detector-bridge analysis evaluated metadata-assisted selection, first detection, and one learned GroundingDINO plug-in through the same lifting interface, exposing query, domain, and adapter-label failure modes rather than a detector leaderboard. In the YCB-V/BOP probe, the tested GroundingDINO route improved from 23.8\% success with generic prompts to 61.4\% with true object-name prompts, while oracle-mask lifting reached 99.97\% and oracle 2D boxes with trimmed crop median reached 79.9\% at 8 cm. A scripted execution audit failed the oracle gate; therefore, the benchmark is positioned as a target-generation diagnostic, not a closed-loop policy or real-robot benchmark.
\end{abstract}

\section{Introduction}
\input{\srroot/sections/introduction}

\section{Related Work}
\input{\srroot/sections/related_work}

\section{Results}
\input{\srroot/sections/results}

\section{Discussion}
\input{\srroot/sections/discussion}

\section{Methods}
\input{\srroot/sections/methods}

\section{Data Availability}
\input{\srroot/sections/data_availability}

\section{Code Availability}
\input{\srroot/sections/code_availability}

\section{Author Contributions}
Z.C. is the sole author and corresponding author. Z.C. conceived the study, designed and implemented the benchmark, ran the experiments, analyzed the data, prepared the figures and tables, and wrote the manuscript.

\section{Competing Interests}
The author declares no competing interests.

\section{Funding}
The author received no specific funding for this work.

\section{Acknowledgements}
The author acknowledges the open-source software and public dataset communities whose tools and datasets made the reproducible analyses possible, including ManiSkill, YCB-V/BOP, and GroundingDINO.

\bibliographystyle{unsrtnat}
\bibliography{\srroot/references}

\end{document}
