The main evidence supports a focused claim: parameterized simulation stress tests can reveal target-generation failures that are hidden by clean-setting success rates. The result is strongest for diagnostic target generation and detector transfer, not for end-to-end closed-loop manipulation. This distinction matters because the benchmark is designed to isolate the language-to-target stage before policy execution.

The threshold analysis changes the interpretation of the RGB-D baselines. Crop-median depth should not be described as universally strongest. It is stronger at the default and relaxed thresholds, while box-center depth is more precise under strict thresholds. This precision--robustness tradeoff is useful because it tells benchmark users which target sources are likely to fail when tolerances change.

The learned-detector bridge also narrows the language-conditioned claim. Metadata-assisted query-aware selection is a controlled comparator, first detection is a stress-sensitive comparator, and GroundingDINO is one learned open-vocabulary detector plug-in tested through the same interface. The YCB/clutter query audit is negative but informative: the generic detector route and current adapter labels do not resolve the harder YCB/clutter setting in this setup. The query ablation further shows that prompt specificity can improve some rows without closing the gap to oracle controls. The benchmark should expose such query, domain, and adapter-metadata failures explicitly rather than masking them behind metadata-only evaluation.

The YCB-V/BOP external RGB-D probe adds an important scope check. It shows that the same target-generation protocol can be applied outside ManiSkill, with ground-truth visible masks and boxes used to separate RGB-D lifting from detector/query localization. The result does not turn the study into a real-robot benchmark, but it reduces the risk that the main conclusion is only a simulator artifact: oracle masks are nearly perfect, oracle 2D boxes expose lifting error, and GroundingDINO improves substantially when prompted with true object names rather than a generic target-object phrase. Repeating the full probe at lower and higher GroundingDINO box/text thresholds preserves the same ordering, so the external detector-query conclusion is not tied to one post-processing threshold.

The closed-loop smoke result is the largest remaining limitation. Although diagnostic success is useful for target-generation analysis, the present scripted executor did not pass the oracle task-success gate. This prevents a positive claim that target-distance success is already calibrated to actual task success. Future work should add a validated scripted or learned executor, then report agreement, target-error bins, and task-success prediction under the same seed splits.

Other limitations are also deliberate. The manipulation stress tests are simulation-based, and the external YCB-V/BOP experiment is a real RGB-D target-generation probe rather than a real-robot execution result. The study therefore does not claim real-robot robustness. It does not evaluate state-of-the-art VLA policies such as RT-style or OpenVLA-style controllers. It does not claim that GroundingDINO is the best open-vocabulary detector or that the current prompt configuration is optimal. These boundaries keep the contribution centered on reproducible diagnosis rather than on policy benchmarking or detector leaderboards.
