\subsection{Episode definition}

An episode is defined as
\[
(T, o^\star, q, D, s, g, \phi, \ell, r),
\]
where \(T\) is the simulator task, \(o^\star\) is the target object, \(q\) is the language query, \(D\) is the detection list, \(s\) is the selector or detector, \(g\) is the RGB-D target source, \(\phi\) is the stressor family, \(\ell\) is the stress level, and \(r\) is the seed. The output is a 3D target, diagnostic success, target-error distance, failure type, and auxiliary detector fields when available.

\subsection{Target sources}

The oracle target uses privileged simulator geometry and is used only to estimate feasibility. Box-center depth projects the selected detection center through the depth map. Crop-median depth takes the median valid depth inside the selected crop. Crop-trimmed median depth removes the lowest and highest 10\% of valid crop depths before taking the median, providing a stronger inlier-style RGB-D baseline without adding a new external model dependency. Crop-top-surface is retained as a deliberately simple heuristic in the larger diagnostic sweeps.

\subsection{Selectors and detector bridge}

The metadata query-aware selector uses simulator-provided labels and metadata to select the target detection, and is treated as a controlled metadata-assisted upper-bound comparator rather than deployed perception. It can still fail when query templates and exposed metadata define different targets or when the stressed detection list lacks a target-consistent entry. The first-detection selector selects the first available detection and is used to expose list-order and distractor sensitivity. The GroundingDINO bridge is a learned open-vocabulary detector plug-in; it reports detection availability, IoU summaries when debug fields are present, and detection-unavailable labels when no usable detection is returned.

\subsection{Stressor families}

Stressors are grouped into detection-list semantic ambiguity, visual, geometric, and target-displacement families. The same-shape, same-color, and nearby stressors manipulate detection-list ordering and crop ambiguity; they are not claimed to be physically inserted scene objects unless accompanied by rendered scene evidence. Visual and geometric stressors perturb occlusion, depth sparsity, depth noise, and camera pose. Target-displacement stressors perturb the target after generation to audit tolerance to downstream offset. The exact level values are generated from YAML configuration files and reported in Supplementary Table S1.

\subsection{Metrics and confidence intervals}

Diagnostic success is computed from the 3D target-error threshold, with 0.08 m as the default. Threshold sensitivity recomputes success at 0.04 m, 0.06 m, 0.08 m, and 0.10 m from stored target-error values. Oracle gap is
\[
\mathrm{gap}(g)=\mathrm{SR}(\mathrm{oracle})-\mathrm{SR}(g),
\]
where \(\mathrm{SR}\) is diagnostic success rate. Oracle rows use privileged simulator target geometry, but they are still evaluated with the same threshold and stressor protocol as non-oracle rows. Oracle success can therefore be below one under hard target-displacement, projection, visibility, or threshold conditions.

Uncertainty estimates are descriptive confidence intervals rather than a multiple-testing framework. For ManiSkill diagnostic sweeps and detector-bridge rows, intervals use seed-block percentile bootstrap aggregation with 2,000 resamples, so all episodes sharing a seed are resampled as a block. For selected detector/selector comparisons with matched seeds, paired effects are computed per seed and bootstrapped with 2,000 paired seed-block resamples. For the external YCB-V/BOP probe, multiple object records can share the same RGB-D frame. We therefore compute confidence intervals by resampling \((\mathrm{scene\_id}, \mathrm{image\_id})\) frame blocks with 1,000 percentile bootstrap resamples rather than treating all detector-target rows as independent records. The reported point estimates are computed over all eligible object-instance rows, while the confidence intervals summarize frame-block variability. The closed-loop oracle-gate audit uses Wilson 95\% intervals for binomial task-success rates. Unless explicitly stated, the manuscript reports estimation and robustness analyses rather than null-hypothesis significance tests.

\subsection{Result generation and audit}

All numerical tables in this draft are generated from JSON or CSV artifacts. The result-to-claim gate records completed episode counts, duplicate counts, runner exceptions, and whether each intended claim is supported. The closed-loop smoke test is included as an audit because it completed technically but failed the oracle execution gate.

\subsection{External RGB-D validation probe}

The external RGB-D probe uses YCB-V/BOP RGB-D frames with ground-truth visible masks, visible 2D boxes, camera intrinsics, and object names. For each selected object instance, the median valid 3D point inside the ground-truth visible mask is treated as the reference target. Oracle-mask rows replay this reference as a consistency control. Oracle-2D-box rows lift the ground-truth visible box through box-center, crop-median, and crop-trimmed-median depth sources. First-ground-truth-box rows test a list-order control, and GroundingDINO rows test generic, true-name, and photo true-name prompts with the same lifting functions. This probe is used only for external target-generation validation; it is not a real-robot or closed-loop manipulation experiment. The full probe is repeated under three GroundingDINO post-processing settings, with box/text thresholds of 0.10/0.10, 0.20/0.20, and 0.30/0.25, to test whether the detector-query conclusion depends on a single threshold choice.
