\documentclass[10pt]{article}
\usepackage[a4paper,margin=0.78in]{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{url}
\usepackage[numbers,sort&compress]{natbib}

\makeatletter
\IfFileExists{sections/introduction.tex}
  {\newcommand{\srroot}{.}}
  {\IfFileExists{scientific_reports/sections/introduction.tex}
    {\newcommand{\srroot}{scientific_reports}}
    {\newcommand{\srroot}{paper/scientific_reports}}}
\def\input@path{{\srroot/}{\srroot/sections/}{\srroot/tables/}}
\makeatother
\graphicspath{{\srroot/}{\srroot/figures/}}

\title{EmbodiedStressBench: A Reproducible Simulation Diagnostic for Query-Conditioned 3D Target Localization in Robotic Manipulation}
\author{Zhuo Chen\\Correspondence: \href{mailto:zhuoc@chalmers.se}{zhuoc@chalmers.se}}
\date{}

\begin{document}
\maketitle

\begin{abstract}
Language-conditioned manipulation systems can hide target-generation failures behind aggregate task success. We present EmbodiedStressBench, a reproducible diagnostic study for stress-testing the language-query-to-3D-target stage of robotic manipulation. The study separates detection-list target selection, RGB-D target lifting, depth and occlusion corruption, and target-displacement tolerance through parameterized stressors, per-episode artifacts, oracle-gap analysis, and a failure taxonomy. Across large-scale ManiSkill diagnostic sweeps, target sources show a precision--robustness tradeoff: box-center depth is more precise under strict distance thresholds, while crop-median depth is stronger at the default and relaxed thresholds. A learned-detector bridge shows that open-vocabulary detectors can be evaluated through the same protocol, and YCB/clutter query checks expose detector-query and adapter-label failure modes without relying on positive closed-loop task-success claims. To reduce the risk of a simulation-only artifact, we additionally evaluate the same target-generation protocol on YCB-V/BOP RGB-D frames with ground-truth masks and boxes: oracle-mask lifting reaches 99.97\% success at 8 cm, oracle 2D boxes with crop-trimmed median depth reach 79.9\%, and GroundingDINO improves from 23.8\% with generic prompts to 61.4\% with true object-name prompts. A scripted closed-loop smoke test did not pass the oracle execution gate, so execution calibration is treated as an unresolved limitation. EmbodiedStressBench is therefore positioned as a detector-agnostic diagnostic substrate for reproducible query-conditioned 3D target-localization failure analysis, not as a closed-loop policy benchmark or real-robot system.
\end{abstract}

\section{Introduction}
\input{\srroot/sections/introduction}

\section{Related Work}
\input{\srroot/sections/related_work}

\section{Results}
\input{\srroot/sections/results}

\section{Discussion}
\input{\srroot/sections/discussion}

\section{Methods}
\input{\srroot/sections/methods}

\section{Data Availability}
\input{\srroot/sections/data_availability}

\section{Code Availability}
\input{\srroot/sections/code_availability}

\section{Author Contributions}
Z.C. is the sole author and corresponding author. Z.C. conceived the study, designed and implemented the benchmark, ran the experiments, analyzed the data, prepared the figures and tables, and wrote the manuscript.

\section{Competing Interests}
The author declares no competing interests.

\section{Funding}
The author received no specific funding for this work.

\section{Acknowledgements}
The author acknowledges the open-source software and public dataset communities whose tools and datasets made the reproducible analyses possible, including ManiSkill, YCB-V/BOP, and GroundingDINO.

\bibliographystyle{unsrtnat}
\bibliography{\srroot/references}

\end{document}
